|

### 2022-05-15 Memo/memo.Rmd
typo
partial revision

In response to comments from Reviewer 1, we have revised our Methods section to
clarify our selection of independent variables, including the use of dummy
variables to improve the accuracy of our estimates, and to provide further
information about our online survey. Additionally, we have included a new
section in the Supplemental Materials to explain how we conducted our survey
and how it contributes to our results. We believe these addition also give the
paper a better theoretical frame to help readers sort through the (many)
results we present.

@@

\textbf{TO DO.}

>>>>

In response to comments from Reviewer 1, we have revised our Methods section to
clarify our selection of independent variables, including the use of dummy
variables to improve the accuracy of our estimates, and to provide further
information about our online survey. Additionally, we have included a new
section in the Supplemental Materials to explain how we conducted our survey
and how it contributes to our results. We believe these additions also give the
paper a better theoretical frame to help readers sort through the (many)
results we present.

@@

We thank Reviewer 1 for the opportunity to clarify the selection of the control variables in our empirical analysis. The inclusion of control variables in our model has two purposes. The first one is to improving the consistency of the estimates. In section XXXX of the appendix, we show by simulation that adding controls improve the consistency of the point estimate, for several distributions of the running variables. In the section XXXX of the appendix, we show that for our data, it improves consistency significantly in both the main estimates and the placebo one. Table XXXX in section XXXX (reproduced below), shows that without controls, the estimated treatment effect is overXXXX and underXXXX. The reason for this improvement is that having control variables make the subpopulations more comparable across thresholds.

XXXX PUT TABLE HERE

The second reason, per \citet{calonico2019regression} results, is that adding control variables improve efficiency in the estimates. Adding XXXX and XXXX, XXXX.

To reflect these informations, we rewrote paragraph XXXX in section XXXX of the main text to:

``XXXX''
